### 2015-09-14 vmcai-2016-tex/abstract.tex
Changes with Ben

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state.  A fundamental
problem with using these guarded value sets is the inability to
generate test inputs in a manner similar to symbolic execution based
analyses.
%is the creation of test inputs for
%program analyses that accept symbolic reference input
%parameters.
Although several solutions have been proposed, none have been proven
to be sound and complete with respect to the heap properties provable
by generalized symbolic execution (GSE). This work presents a method for initializing input references
in a symbolic input heap using guarded value sets that exactly
preserves GSE semantics. A correctness proof for the initialization
scheme is provided with a proof-of-concept implementation. Results from an empirical evaluation on a standard set of \gsetxt{} benchmarks show an increase in the
size and number of analyzed heaps over existing GSE
representations. The initialization technique can be used to ensure
that guarded value set based symbolic execution engines operate in a
provably correct manner with regards to symbolic references as well as
provide the ability to generate concrete heaps that serve as test
inputs to the program.

>>>>

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state.  A fundamental
problem with using these guarded value sets is the inability to
generate test inputs in a manner similar to symbolic execution based
analyses.
%is the creation of test inputs for
%program analyses that accept symbolic reference input
%parameters.
Although several solutions have been proposed, none have been proven
to be sound and complete with respect to the heap properties provable
by generalized symbolic execution (GSE). This work presents a method for initializing input references
in a symbolic input heap using guarded value sets that exactly
preserves GSE semantics. A correctness proof for the initialization
scheme is provided with a proof-of-concept implementation. Results from an empirical evaluation on a command set of \gsetxt{} data structure benchmarks show an increase in the
size and number of analyzed heaps over existing GSE
representations. The initialization technique can be used to ensure
that guarded value set based symbolic execution engines operate in a
provably correct manner with regards to symbolic references as well as
provide the ability to generate concrete heaps that serve as test
inputs to the program.

### 2015-09-14 vmcai-2016-tex/bisimulation.tex
Changes with Ben

The theorems assert the existence of a
bisimulation between sets of states related by~\gsetxt{} ($p \rgse
p^\prime$) and states related by the symbolic heap and update rules in this paper ($q \rsym
q^\prime$). The relations are on the universe of \emph{well-formed}
states $S$, which have the properties in \secref{sec:sh} with the
constraint that the states are \emph{feasible}: successors exist
unless at \cfgt{end}. Let $p \rgse p^\prime$ be a union over relations
for~\gsetxt{} (see~\cite{Hillery:2015}): $\rgse = \rgse^\mathit{A} \cup
\rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup
\rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup
\rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access
after evaluating the expression for the base reference $\lp
\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$, \emph{W} is
a field write after evaluating the expression for the right operand
$\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the
left and right operands $\lp \cfgnt{v}\ \cfgt{=}\ \cfgnt{*}
\rightarrow \cfgnt{k}\rp$, the prime symbol indicates a null reference
in the operation or a false outcome, and \emph{\com} is everything
else in the language. Any state relation, say $\rightarrow_x$, is
trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Leftrightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
The relation captures the notion of splitting groups of heaps at
certain operations. For example, suppose a set $P$ contains a single state $p$
with all references uninitialized. If $p$ is a field access state, it has two
potential successors in~\gsetxt{}: a non-null reference and a null reference. 
Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.

The functional equivalence between heaps in states $p$
and $q$ requires both a mapping to relate the two heaps and a
constraint on the feasibility of that mapping in the presence of a
path constraint from symbolic execution. Subscripts indicate state tuple
members as in $p = (
\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$.
\begin{definition}
\label{def:homomorphism}
A \textbf{homomorphism}, given the universe of field indices $\mathcal{F}$ and the universe of locations $\mathcal{L}$, is 
$$
\begin{array}{l}
 s_p \rightharpoonup_{h} s_q \Leftrightarrow 
\exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \forall \phi_\alpha\ (\\ 
\ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
\ \ \ \ \ \ \ \ \exists \phi_\beta\ ( (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ 
 )) ) ) ) )
\end{array}
$$
\end{definition}
\begin{definition}
\label{def:hc}
The \textbf{homomorphism constraint} is
%\begin{align*}
\[
\mathbb{HC}(p \rightharpoonup_{h} q) = 
\bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\}
\]
%\end{align*}
\end{definition}
Functional equivalence asserts a common structure in the two heaps under certain
conditions. It is used to relate states in $p \rgse
p^\prime$ to states in $q \rsym q^\prime$.
\begin{definition}
\label{representation}
States $(p\ q)$ are in the \textbf{representation relation}, $p \sqsubset q$, if and only if, $\eta_p = \eta_q ,\ \cfgnt{e}_p =
\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
homomorphism $p \rightharpoonup_{h} q$
such that $\mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) )$.
The represented relation is extended to sets of states $P$ and a single state $q$ as
$P \sqsubset q \Longleftrightarrow \forall p\ (p \sqsubset q \Leftrightarrow p \in P)$.
\end{definition}
The statement $p \sqsubset q$ ensures that a functionally equivalent
heap to the one in $p$ is present, by the homomorphism, and valid, by
the heap constraint and path constraint, in $q$. As the states in $P$
are only differentiated by heaps and those states are only
differentiated from $q$ by both the heap and path constraint in $q$,
$P \sqsubset q$ implies that $q$ is representative of all the states
in $P$ up to the given point of execution expressed in $\phi_q$.
\begin{definition}
\label{bisimulation}
The \textbf{functional associated to bisimulation} applied to $\sqsubset$, denoted as $F_\sim(\sqsubset)$, is the set of all pairs
$(P\ q)$ such that
\begin{equation}
\label{eqn:BisimulationForwards}
\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists q^\prime\ ( q \rsym q^\prime \wedge P^\prime\ \sqsubset\ q^\prime))
\end{equation}
\begin{equation}
\label{eqn:BisimulationBackwards}
\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists P^\prime\ ( P \rsgse P^\prime \wedge P^\prime\ \sqsubset\ q^\prime))
\end{equation}
If $\sqsubset$ is a bisimulation, then the greatest fixed point of $F_\sim(\sqsubset)$ is the bisimilarity relation denoted by $\sim$.
\end{definition}
Although the functional reasons over a forward and backward
simulation as typical~ \cite{Sangiorgi:2011}, its use of a meta-relation, $\rsgse$, is unique.

>>>>

The theorems assert the existence of a
bisimulation between sets of states related by~\gsetxt{} ($p \rgse
p^\prime$) and states related by the symbolic heap and update rules in this paper ($q \rsym
q^\prime$). The relations are on the universe of \emph{well-formed}
states $S$, which have the properties in \secref{sec:sh} with the
constraint that the states are \emph{feasible}: successors exist
unless at \cfgt{end}. Let $p \rgse p^\prime$ be a union over relations
for~\gsetxt{} (see~\cite{Hillery:2015}): $\rgse = \rgse^\mathit{A} \cup
\rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup
\rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup
\rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access
after evaluating the expression for the base reference $\lp
\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$, \emph{W} is
a field write after evaluating the expression for the right operand
$\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the
left and right operands $\lp \cfgnt{v}\ \cfgt{=}\ \cfgnt{*}
\rightarrow \cfgnt{k}\rp$, the prime symbol indicates a null reference
in the operation or a false outcome, and \emph{\com} is everything
else in the language. Any state relation, say $\rightarrow_x^Y$, is
trivially extended to sets of states as
$$
P \hookrightarrow_x^Y P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x^Y p^\prime \Leftrightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
The relation captures the notion of splitting groups of heaps at
certain operations. For example, suppose a set $P$ contains a single state $p$
with all references uninitialized. If $p$ is a field access state, it has two
potential successors in~\gsetxt{}: a non-null reference and a null reference. 
Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.

The functional equivalence between heaps in states $p$
and $q$ requires both a mapping to relate the two heaps and a
constraint on the feasibility of that mapping in the presence of a
path constraint from symbolic execution. Subscripts indicate state tuple
members as in $p = (
\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$.
\begin{definition}
\label{def:homomorphism}
A \textbf{homomorphism}, given the universe of field indices $\mathcal{F}$ and the universe of locations $\mathcal{L}$, is 
$$
\begin{array}{l}
 s_p \rightharpoonup_{h} s_q \Leftrightarrow 
\exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \forall \phi_\alpha\ (\\ 
\ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
\ \ \ \ \ \ \ \ \exists \phi_\beta\ ( (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ 
 )) ) ) ) )
\end{array}
$$
\end{definition}
\begin{definition}
\label{def:hc}
The \textbf{homomorphism constraint} is
%\begin{align*}
\[
\mathbb{HC}(p \rightharpoonup_{h} q) = 
\bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\}
\]
%\end{align*}
\end{definition}
The notation $\cfgnt{L}_p^\rightarrow$ denotes the image of $\cfgnt{L}_p$. Functional equivalence asserts a common structure in the two heaps under certain
conditions. It is used to relate states in $p \rgse
p^\prime$ to states in $q \rsym q^\prime$.
\begin{definition}
\label{representation}
States $(p\ q)$ are in the \textbf{representation relation}, $p \sqsubset q$, if and only if, $\eta_p = \eta_q ,\ \cfgnt{e}_p =
\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
homomorphism $p \rightharpoonup_{h} q$
such that $\mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) )$.
The represented relation is extended to sets of states $P$ and a single state $q$ as
$P \sqsubset q \Longleftrightarrow \forall p\ (p \sqsubset q \Leftrightarrow p \in P)$.
\end{definition}
The statement $p \sqsubset q$ ensures that a functionally equivalent
heap to the one in $p$ is present, by the homomorphism, and valid, by
the heap constraint and path constraint, in $q$. As the states in $P$
are only differentiated by heaps and those states are only
differentiated from $q$ by both the heap and path constraint in $q$,
$P \sqsubset q$ implies that $q$ is representative of all the states
in $P$ up to the given point of execution expressed in $\phi_q$.
\begin{definition}
\label{bisimulation}
The \textbf{functional associated to bisimulation} applied to $\sqsubset$, denoted as $F_\sim(\sqsubset)$, is the set of all pairs
$(P\ q)$ such that
\begin{equation}
\label{eqn:BisimulationForwards}
\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists q^\prime\ ( q \rsym q^\prime \wedge P^\prime\ \sqsubset\ q^\prime))
\end{equation}
\begin{equation}
\label{eqn:BisimulationBackwards}
\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists P^\prime\ ( P \rsgse P^\prime \wedge P^\prime\ \sqsubset\ q^\prime))
\end{equation}
If $\sqsubset$ is a bisimulation, then the greatest fixed point of $F_\sim(\sqsubset)$ is the bisimilarity relation denoted by $\sim$.
\end{definition}
Other than the use of a meta-relation, $\rsgse$, \defref{bisimulation} reasons over the typical forward and backward
simulation~\cite{Sangiorgi:2011}.

### 2015-09-14 vmcai-2016-tex/evaluation.tex
Changes with Ben

%\subsection{Analysis}
The \symtxt{} algorithm is implemented as an extension to the Symbolic
PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13}
framework. In addition to the operations presented in this paper, the
implementation contains support for operations over integers,
calculating per-path preconditions and postconditions, as well as
generating test input heaps that exercise all feasible control flow
paths. We are currently working on adding support for floating point
operations, arrays, and bit-operations. The \symtxt{} implementation
uses the \texttt{jConstraints}
library~\cite{ase2014-ghilrr,jpf2014-dghirr} to encode the heap
constraints and the z3 solver~\cite{deMouraBjorner08Z3} as the
underlying constraint solver. We leverage the incremental solving
feature in z3 in our experiments. We also implement other
optimizations that cache and re-use solutions to previous
constraints. These optimizations are an important part of our
implementation because only small portions of the heap constraint
change during execution.

>>>>

%\subsection{Analysis}
The \symtxt{} algorithm is implemented as an extension to the Symbolic
PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13}
framework. In addition to the operations presented in this paper, the
implementation contains support for operations over integers,
calculating per-path preconditions and postconditions, as well as
generating test input heaps that exercise all feasible control flow
paths. Future work is adding support for floating point
operations, arrays, and bit-operations.

The \symtxt{} implementation uses \texttt{jConstraints} with the z3 solver \cite{ase2014-ghilrr,jpf2014-dghirr,deMouraBjorner08Z3}. The implementation takes advantage of incremental solving and employs caching for performance since only small portions of the heap constraint changes during the search.

### 2015-09-14 vmcai-2016-tex/intro.tex
Changes with Ben

Precisely modeling operations on unconstrained heaps
is challenging because it requires formulating logical predicates over
an input domain that contains a potentially unbounded number of hidden
references~\cite{Chen:2013,Qu:2011}. Generalized symbolic execution
(\gsetxt{}), and its variants, provide an accurate
solution, but they quickly produce an overwhelming number of execution
paths for all but the simplest heap shapes \cite{GSE03,Deng:2007}. Efforts to
extend~\gsetxt{} principles to guarded value sets have failed to
produce provably equivalent results \cite{LISTEFFORTS}. Thus, despite
the advantages of using guarded value sets, it remains an open
question to how they can be used in symbolic execution to automatically
model all possible program behaviors in the case of an arbitrary input
heap.

@@

A proof-of-concept implementation of symbolic initialization is
reported in this paper. The implementation is for Java in the Java
Pathfinder tool. It demonstrates on a standard set of benchmarks for GSE evaluation (\cite{PAPERSESTABLISHINGBENCHMARKSET}) an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods. Although guarded value
sets require extra interaction with an SMT solver, the
savings in representing multiple heap shapes in a single
structure can overcome the cost of the solver calls. For the tree structures in the standard benchmarks, the
comparison shows an exponential increase in the number of heaps that
can be analyzed, meaning that other
approaches based on~\gsetxt\ fail to complete in the allotted time.

>>>>

Precisely modeling operations on unconstrained heaps
is challenging because it requires formulating logical predicates over
an input domain that contains a potentially unbounded number of hidden
references~\cite{Chen:2013,Qu:2011}. Generalized symbolic execution
(\gsetxt{}), and its variants, provide an accurate
solution, but they quickly produce an overwhelming number of execution
paths for all but the simplest heap shapes \cite{GSE03,Deng:2007}. Efforts to
extend~\gsetxt{} principles to guarded value sets have yet to
produce provably equivalent results \cite{LISTOFEFFORTS}. Thus, despite
the advantages of using guarded value sets, it remains an open
question to how they can be used in symbolic execution to automatically
model all possible program behaviors in the case of an arbitrary input
heap.

@@

A proof-of-concept implementation of symbolic initialization is
reported in this paper. The implementation is for Java in the Java
Pathfinder tool. It demonstrates on a command set of data structure benchmarks for GSE evaluation (\cite{PAPERSESTABLISHINGBENCHMARKSET}) an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods. Although guarded value
sets require extra interaction with an SMT solver, the
savings in representing multiple heap shapes in a single
structure can overcome the cost of the solver calls. For the tree structures in the standard benchmarks, the
comparison shows an exponential increase in the number of heaps that
can be analyzed, meaning that other
approaches based on~\gsetxt\ fail to complete in the allotted time.

### 2015-09-14 vmcai-2016-tex/summary-heap.tex
Changes with Ben

\section{A Symbolic Heap}
A \emph{symbolic heap}, as defined in this work, is a pair
$(\cfgnt{L}\ \cfgnt{R})$, indicating a \emph{location map}
$\cfgnt{L}$ and a \emph{reference map} $\cfgnt{R}$.  Given a reference $r$ in the heap,
$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
associated with $r$. The constraint associated with each
location is a guard representing the conditions under which the
associated reference maps to the given location. By definition, any
location appears at most once in any given value set. Unions of value
sets containing the same location are resolved by forming a
disjunction of the constraints from each set. $\cfgnt{R}(\cfgnt{l},
\cfgnt{f}) = \cfgnt{r}$ is the reference associated with the given
location-field pair in the heap.

@@

@@

A \emph{well-formed} symbolic heap is \emph{deterministic} and \emph{type consistent}. Determinism means a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$.
Type consistent means that all locations in a guarded value set from a reference have the same type\footnote{Although not treated in this presentation, the concept naturally extends to polymorphic languages}:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$

@@

The machine state $\cfgnt{s}$ includes the program
registry $\mu$, the symbolic heap, the~\emph{path condition} $\phi$, the \emph{environment} $\eta$, the current expression (i.e., program), and the continuation $\cfgnt{k}$. The registry never changes so it is
omitted from the state tuple in the rest of the presentation. The path condition is a predicate of the program variables. 
The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is the same as $\eta$ except that
the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. This notation is used with symbolic heaps as well.

The continuation
$\cfgnt{k}$ indicates with the symbol $\cfgnt{*}$ where the expression $\cfgnt{e}$ came from, stores
temporary computation, and keeps track of the next continuation. For
example, the continuation $\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$ indicates that the machine is evaluating the
expression for the object reference on which the field $\cfgnt{f}$ is
going to be accessed. Once the field access is complete, the machine
continues with $\cfgnt{k}$.

>>>>

\section{A Symbolic Heap}
A \emph{symbolic heap}, as defined in this work, is a tuple
$(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, indicating a \emph{location map}
$\cfgnt{L}$, a \emph{reference map} $\cfgnt{R}$, a \emph{path condition} $\phi$, and an \emph{environment} $\eta$.  Given a reference $r$ in the heap,
$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
associated with $r$. The constraint associated with each
location is a guard representing the conditions under which the
associated reference maps to the given location. By definition, any
location appears at most once in any given value set. Unions of value
sets containing the same location are resolved by forming a
disjunction of the constraints from each set. $\cfgnt{R}(\cfgnt{l},
\cfgnt{f}) = \cfgnt{r}$ is the reference associated with the given
location-field pair in the heap.

@@

The path condition is a predicate of the program variables. The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is the same as $\eta$ except that
the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. This notation for update is used with $\cfgnt{L}$ and $\cfgnt{R}$ as well.

@@

A \emph{well-formed} symbolic heap is \emph{deterministic} and \emph{type consistent}. Determinism means a reference in $(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$.
Type consistent means that all locations in a guarded value set from a reference have the same type\footnote{Although not treated in this presentation, the concept naturally extends to polymorphic languages}:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$

@@

The machine state $\cfgnt{s}$ includes the program
registry $\mu$, the symbolic heap, the current expression (i.e., program), and the continuation $\cfgnt{k}$. The registry never changes so it is
omitted from the state tuple in the rest of the presentation. The continuation
$\cfgnt{k}$ indicates with the symbol $\cfgnt{*}$ where the expression $\cfgnt{e}$ came from, stores
temporary computation, and keeps track of the next continuation. For
example, the continuation $\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$ indicates that the machine is evaluating the
expression for the object reference on which the field $\cfgnt{f}$ is
going to be accessed. Once the field access is complete, the machine
continues with $\cfgnt{k}$.
